### 2014-02-24 paper/retrofit.tex
New world syntax!
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Typing judgment: $|tyrule tG tS te tt|$

\begin{mathpar}
\and
\inferrule[T-evalCtx]
{| conf tS te -> conf tS' te')|}
{| conf tS (intE te) -> conf tS' (intE te') |}

@@

ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |lconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &|erase il (send ie1 ie2 ie3) =| \begin{cases}
    |send ie1 ie2 bullet| & |ie2 cantFlowTo il| \\
    |send ie1 ie2 (erase il ie3)| & \text{otherwise}
  \end{cases} \\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

\begin{figure}
\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (lconf id il tS (iniE ie), ldots)
.->
iS' ; sched step (lconf id il' tS (iniE ie'), ldots)
|}

\and
\inferrule[I-done]
{|
|}
{|
iconf iS (lconf id il tS iv, ldots)
.->
iS ; sched done (lconf id il tS iv, ldots)
|}

\and
\inferrule[I-stepT]
{|
conf tS (te) -> conf tS' te'
|}
{|
iconf iS (lconf id il tS (iniE (IT te)), ldots)
.->
iS ; sched step (lconf id il tS' (iniE (IT te')), ldots)
|}

\and
\inferrule[I-noStepT]
{|
conf tS (te) -/> 
|}
{|
iconf iS (lconf id il tS (iniE (IT te)), ldots)
.->
iS ; sched noStep (lconf id il tS (iniE (IT te)), ldots)
|}

\and
\inferrule[I-noStep]
{|
it .-/> 
|}
{|
iconf iS (it, ldots)
.->
iS ; sched noStep (it, ldots)
|}

\and
\inferrule[I-getLabel]
{ }
{|
iconf iS (tconf id il getLabel)
.->
iconf iS (tconf id il il)
|}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (tconf id il (setLabel il'))
.->
iconf iS (tconf id il' unit)
|}

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = lconf id il tS (iniE id')|\\
|itnew = lconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (lconf id il tS (iniE (fork ie)), ldots)
.->
iS'; sched fork (it1, ldots, itnew)
|}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
iconf iS  (tconf id il (send id' il' ie))
.->
iconf iS' (tconf id il unit)
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
}
{|
iconf iS  (tconf id il (ix1, ix2 <= recv. ie1 ie2))
.->
iconf iS' (tconf id il ({ie'/ix1,id'/ix2} ie1))
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS  (tconf id il (ix1, ix2 <= recv. ie1 ie2))
.->
iconf iS' (tconf id il ie2)
|}

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |iconf iS (tconf id il (il1 lop il2)) .-> iconf iS (tconf id il iv)| }

\and
\inferrule[I-border]
{ }
{|
iconf iS (tconf id il (IT (TI (ie))))
.->
iconf iS (tconf id il ie)
|}

\and
\inferrule[T-border]
{ } {| conf tS (intE (TI (IT (te)))) -> conf tS (intE te)|}
\end{mathpar}
\caption{IFC language and general embedding.}
\label{fig:ifc}
\end{figure}

>>>>

Typing judgment: $|tyrule tG tS te tty|$

\begin{mathpar}

@@

ix1, ix2 <= brecv . ie @= IT (let tx = TI (ix1, ix2 <= recv. ie  (IT tx)) in tx)

conf tS te @= iconf iS (fullconf id il tS (iniEt te), ldots)
niconf iS id il ie @= iconf iS (fullconf id il tS (iniEi ie), ldots)
\end{code}
\caption{IFC grammar.}
\label{fig:ifc-grammar}
\end{figure}

\begin{figure}
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))| \\
  &|erase il (tconf id il' ie) =| \begin{cases}
    %|lconf bullet bullet bullet bullet| & |il' cantFlowTo il| \\
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase il tS) (erase il ie)| & \text{otherwise}
  \end{cases} \\
  %&|erase il iS [i mapsto Q] = iS [i mapsto (erase il Q)]|\\
  &|erase il Q = filter il Q|\\
  &|erase il (send ie1 ie2 ie3) =| \begin{cases}
    |send ie1 ie2 bullet| & |ie2 cantFlowTo il| \\
    |send ie1 ie2 (erase il ie3)| & \text{otherwise}
  \end{cases} \\
  &\text{In all other cases, |erasef il| is applied homomorphically.}
\end{align*}
\caption{Erasure function.}
\end{figure}

\begin{figure}
\begin{mathpar}
\and
\inferrule[I-done]
{|
|}
{|
iconf iS (fullconf id il tS iv, ldots)
.->
iS ; sched done (fullconf id il tS iv, ldots)
|}

\and
\inferrule[I-noStep]
{|
iconf iS (it, ldots) .-/> 
|}
{|
iconf iS (it, ldots)
.->
iS ; sched noStep (it, ldots)
|}

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (fork ie)), ldots)
.->
iS'; sched fork (it1, ldots, itnew)
|}

\and
\inferrule[I-getLabel]
{ }
{|
niconf iS id il getLabel
.->
niconf iS id il il
|}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
niconf iS id il (setLabel il')
.->
niconf iS id il' unit
|}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
niconf iS  id il (send id' il' ie)
.->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
.->
niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
.->
niconf iS' id il ie2
|}

\inferrule[I-labelOp]
{ |denot (il1 lop il2) = iv|}
{ |niconf iS id il (il1 lop il2) .-> niconf iS id il iv| }

\and
\inferrule[I-border]
{ }
{|
niconf iS id il (IT (TI (ie)))
.->
niconf iS id il ie
|}

\and
\inferrule[T-border]
{ } {| conf tS (TI (IT (te))) -> conf tS te|}
\end{mathpar}
\caption{IFC language and general embedding.}
\label{fig:ifc}
\end{figure}
